---
title: "R Notebook"
output: html_notebook
---

```{r echo=FALSE}
library(tidyverse)
library(tidymodels)
library(skimr)

```


```{r }


train <- read.csv(file="train.csv")

folds <- vfold_cv(train, v = 5)


```

## First look at the data 

We need to predict if people were transported or not (Transported). We have 8 693 passengers. 

### Character variables

- They are leaving from 3 different home planet (HomePlanet) to go to 3 different destination planet (Destination).

- They can do the transport either in or not in (CryoSleep). 35 % are in cryosleep

- They have a cabin number and very few share their cabin with their family resulting in 6560 different (Cabin). 

- They can have VIP status or not (VIP), but only 200 do. 

- They all have different names (Name), but some share the same last name. We could create a famility variable although it could be bias. 

### Numeric variables

- We have a age variable, which median age of 27 and p75 of 38. Overall, a young crowd. 

- We have 5 variables indicating how much someone spent in the different services of the flight. It would be more useful to know how much they spent overall indicating a level of wealth that would more likely still be under VIP status. 

```{r }

skim(train)

train %>% 
  group_by(VIP) %>% 
  count()

train %>% 
  group_by(CryoSleep) %>% 
  count()

```

### Link with outcome 

- It would seem that VIP Status does not predict transport, in fact you are less likely to be transported if you are VIP. 

- Cryosleep seems to predict whether or not they will be transported

- 




```{r }

# train_test <- 
#   train %>% 
#     mutate(LastName = word(Name,2)) %>% 
#   arrange(desc(LastName))
#   

train %>% 
  filter(VIP != "") %>%   
  count(Transported,VIP) %>% 
      group_by(VIP) %>% 
      mutate(proportion = n/sum(n)) %>% 
      ggplot(aes(x=Transported,y=proportion)) +
      geom_col() +
      facet_wrap(~VIP,nrow=2) +
   scale_x_discrete(guide = guide_axis(n.dodge=2)) + 
   labs(title="VIP status")

train %>% 
  filter(CryoSleep != "") %>%   
  count(Transported,CryoSleep) %>% 
      group_by(CryoSleep) %>% 
      mutate(proportion = n/sum(n)) %>% 
      ggplot(aes(x=Transported,y=proportion)) +
      geom_col() +
      facet_wrap(~CryoSleep,nrow=2) +
   scale_x_discrete(guide = guide_axis(n.dodge=2)) + 
   labs(title="Cryosleep")

# train %>% 
#   filter({{var}} != "") %>%   
#   count(Transported,{{var}}) %>% 
#       group_by({{var}}) %>% 
#       mutate(proportion = n/sum(n)) %>% 
#       ggplot(aes(x=Transported,y=proportion)) +
#       geom_col() +
#       facet_wrap(~{{var}},nrow=2) +
#    scale_x_discrete(guide = guide_axis(n.dodge=2)) + 
#    labs(title=title)
#   
# Feature engineering


 # -------Extracting Last -------# 
# train_test <- 
#   train %>% 
#     mutate(LastName = word(Name,2)) %>% 
#   arrange(desc(LastName))
# #   
#     train %>% 
#       mutate(RoomService = case_when(
#         CryoSleep== "True" ~ 0, 
#         TRUE ~  RoomService), 
#         FoodCourt = case_when(
#         CryoSleep== "True" ~ 0, 
#         TRUE ~  FoodCourt), 
#         ShoppingMall = case_when(
#         CryoSleep== "True" ~ 0, 
#         TRUE ~  ShoppingMall), 
#         Spa = case_when(
#         CryoSleep== "True" ~ 0, 
#         TRUE ~  Spa), 
#         VRDeck = case_when(
#         CryoSleep== "True" ~ 0, 
#         TRUE ~  VRDeck), 
#        RoomService = case_when(is.na(RoomService) ~ 0 , 
#                                TRUE ~ RoomService),
#         FoodCourt = case_when(is.na(FoodCourt) ~ 0 , 
#                                TRUE ~ FoodCourt),
#         ShoppingMall = case_when(is.na(ShoppingMall) ~ 0 , 
#                                TRUE ~ ShoppingMall),
#          Spa = case_when(is.na(Spa) ~ 0 , 
#                                TRUE ~ Spa),
#           VRDeck = case_when(is.na(VRDeck) ~ 0 , 
#                                TRUE ~ VRDeck),
#         AllSpending = RoomService + FoodCourt + ShoppingMall + Spa + VRDeck) 
#  #      mutate(CryoSleep = case_when(CryoSleep=="" & AllSpending ~ "True", TRUE ~ CryoSleep))) %>% 
   #   filter(CryoSleep=="")

  
```




